\LaTeX\ Technical Documents with Docker and Make

### 2020-12-08 ms.tex
improve paper

\documentclass[journal]{IEEEtran}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{booktabs}
\usepackage{datatool}
\usepackage{flushend}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{trees}
\usetikzlibrary{fit}
\usetikzlibrary{backgrounds}
\usepackage[hyphens]{url}
\usepackage{hyperref}

@@

The \textit{author} may use the template for writing \textit{documents} in the following way:
\begin{enumerate}
	\item clones the template,
	\item specifies the name of the \textit{document} in the Makefile,
	\item develops the Dockerfile,
	\item develops the \textit{code} in the local repository,
		\begin{enumerate}
			\item develops the fast/draft and slow/final version \textit{document} in \textit{code},
			\item develops the saving/loading of \textit{results} in/from the \textit{tmp} directory,
		\end{enumerate}
	\item executes \textit{make} for generating the fast/draft version \textit{document} used during development and experimentation,
	\item executes \textit{make ARG=-{}-full} for generating the slow/final version \textit{document} used for distribution.
	\item executes \textit{make clean} to restore to a clean state by removing the \textit{tmp} directory,
\end{enumerate}

@@

The template makes use of the automatic generation of intermediate files of the Make program.
The \textit{author} only needs to edit (or use the \textit{touch} POSIX utility to update the modification time) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with Make.

@@

Another useful function for Python is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}).
\begin{lstlisting}[language=python, style=lststyle, caption={Convert Pandas DataFrame to \LaTeX\ table.}]
df = pd.DataFrame(table)
df.to_latex("tmp/metrics.tex", float_format="%.2f")
\end{lstlisting}

@@

In cases where reproducibility checks are required, the POSIX utility \textit{cmp} can be used.
For specifically identifying the sources of non-determinism an author can use tools such as diffoscope\footnote{\url{https://diffoscope.org/}} in the resulting \textit{document} binaries as follows:
\begin{lstlisting}[language=bash, style=lststyle, caption={Test fast/draft document reproducibility.}]
# Generate the first fast/draft document version
make
# Backup the first resulting pdf
cp tmp/ms.pdf tmp/ms-previous.pdf
# Update the modification timestamp of main.py
touch main.py
# Generate the second fast/draft document version
make
# Compare fast/draft document versions byte by byte
cmp tmp/ms.pdf tmp/ms-previous.pdf
# Compare fast/draft document versions
# in a human readable form
diffoscope tmp/ms.pdf tmp/ms-previous.pdf
\end{lstlisting}

\section{Example use case of the template}
This sections provides a use case of the template and also serves as a manual for writing \LaTeX\ \textit{documents} with Python as the \textit{results code} programming language.
We train and test a VGG11 neural network~\cite{simonyan2014very} with batch normalization in PyTorch~\cite{paszke2019pytorch}, on the following datasets:
\begin{itemize}
	\item MNIST~\cite{lecun2010mnist},
	\item FashionMNIST~\cite{xiao2017fashion},
	\item KMNIST~\cite{clanuwat2018deep},
	\item CIFAR10~\cite{krizhevsky2009learning},
	\item CIFAR100~\cite{krizhevsky2009learning} and
	\item SVHN~\cite{netzer2011reading}.
\end{itemize}

We use the default train, validation and test datasets and compare the use of ReLU\cite{dahl2013improving} and SiLU\cite{elfwing2018sigmoid} activation functions in a VGG11 model.
The images from the MNIST variants are resized to $32\times 32$ to comply with the dimensions of VGG11.

@@

Making use of setting the random seeds we consistenly get the same figures as shown in Fig.\ref{fig:image} which depicts the train and validation loss for all datasets.
\begin{figure}[!t]
	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/MNIST-loss.pdf}}
	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/FashionMNIST-loss.pdf}}
	\caption{Train and validation losses for MNIST and FashionMNIST.}
	\label{fig:image}
\end{figure}

@@

\section{Conclusion}
Creation, usage and publication of technical documents are one of the top challenges for reproducible technical documents~\cite{barba2019praxis}.
The proposed template aids to this purpose in writing reproducible technical documents using the tools that most of academics already use (\LaTeX, Docker, Make).

>>>>

\documentclass[journal]{IEEEtran}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{booktabs}
\usepackage{datatool}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{trees}
\usetikzlibrary{fit}
\usetikzlibrary{backgrounds}
\usepackage[hyphens]{url}
\usepackage{hyperref}

@@

The \textit{author} may use the template for writing \textit{documents} in the following way:
\begin{enumerate}
	\item clones the template,
	\item specifies the name of the \textit{document} in the Makefile,
	\item creates and develops the Dockerfile,
	\item creates and develops the \textit{code} in the local repository including code for:
		\begin{enumerate}
			\item generating fast/draft and slow/final version \textit{document} in \textit{code} and
			\item saving/loading the \textit{results} in/from the \textit{tmp} directory,
		\end{enumerate}
	\item executes \textit{make} for generating the fast/draft version \textit{document} used during development and experimentation,
	\item executes \textit{make ARG=-{}-full} for generating the slow/final version \textit{document} used for distribution and
	\item executes \textit{make clean} to restore to a clean state by removing the \textit{tmp} directory.
\end{enumerate}

@@

The template makes use of the automatic generation of intermediate files of the Make program.
The \textit{author} only needs to edit a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with Make.
Forced compilations without change could be done using the \textit{touch} POSIX utility that updates the modification time.

\section{Template utilities}

@@

Another useful function when using Python for \textit{results code} is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}).
\begin{lstlisting}[language=python, style=lststyle, caption={Convert Pandas DataFrame to \LaTeX\ table.}]
df = pd.DataFrame(table)
df.to_latex("tmp/metrics.tex", float_format="%.2f")
\end{lstlisting}

@@

An \textit{author} can use the POSIX utility \textit{cmp} to compare \textit{documents} (generated in a different session, OS or underlying hardware) byte by byte, and diffoscope\footnote{\url{https://diffoscope.org/}} for identifying sources of non-determinism as follows:
\begin{lstlisting}[language=bash, style=lststyle, caption={Test fast/draft document reproducibility.}]
# Generate the first fast/draft document version
make
# Backup the first resulting pdf
cp tmp/ms.pdf tmp/ms-previous.pdf
# Update the modification timestamp of main.py
touch main.py
# Generate the second fast/draft document version
make
# Compare fast/draft document versions byte by byte
cmp tmp/ms.pdf tmp/ms-previous.pdf
# Compare fast/draft document versions
# in a human readable form
diffoscope tmp/ms.pdf tmp/ms-previous.pdf
\end{lstlisting}

\section{Example use case of the template}
This sections provides a use case of the template and also serves as a manual for writing \LaTeX\ \textit{documents} with Python as the \textit{results code} programming language.
We train and test a MobilenetV2 neural network~\cite{sandler2018mobilenetv2} in PyTorch~\cite{paszke2019pytorch}, on the following datasets:
\begin{itemize}
	\item MNIST~\cite{lecun2010mnist},
	\item FashionMNIST~\cite{xiao2017fashion},
	\item KMNIST~\cite{clanuwat2018deep},
	\item CIFAR10~\cite{krizhevsky2009learning},
	\item CIFAR100~\cite{krizhevsky2009learning} and
	\item SVHN~\cite{netzer2011reading}.
\end{itemize}

We use the default train, validation and test datasets and compare the use of ReLU6\cite{dahl2013improving} and SiLU\cite{elfwing2018sigmoid} activation functions in a VGG11 model.
The images from the MNIST variants are resized to $32\times 32$ to comply with the dimensions of VGG11.

@@

Making use of setting the random seeds we consistenly get the same figures as shown in Fig.\ref{fig:image} which depicts the train and validation loss for all datasets.
\begin{figure}[!t]
	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/MNIST-loss.pdf}}
	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/FashionMNIST-loss.pdf}}
	\\
	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/KMNIST-loss.pdf}}
	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/CIFAR10-loss.pdf}}
	\\
	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/CIFAR100-loss.pdf}}
	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/SVHN-loss.pdf}}
	\caption{Comparison of ReLU6 and SiLU train and validation losses for all datasets.}
	\label{fig:image}
\end{figure}

@@

\section{Conclusion}
Creation, usage and publication of technical documents are one of the top challenges for reproducible technical documents~\cite{barba2019praxis}.
The proposed template aids to this purpose in writing reproducible technical documents using the tools that most of academics already use (\LaTeX, Docker, Make) in a portable and efficient way.
